Sketch of DP - Bayesian Inference

### 2018-07-16 main-sketch.tex
typo
fix typos

  \Pr(\theta | \dataobs) = \frac{Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}

@@

\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.

@@

Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias})--

@@

\todo{to check}\]

@@

  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)

>>>>

  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}

@@

$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.

@@

Specifically, we will consider the situation where $\theta$ represents the parameter --(informally called \emph{bias})--

@@

@@

  \Pr(\vtheta|\dataobs)=\dirichlet(\vtheta+\mathbf{z})
